|

### 2025-10-20 manuscript/pre_print.qmd
deleted and cleaned up to have qmd render to pdf with equations working

---
title: |
  Does resting energy expenditure differ between women with and without polycystic ovary syndrome (PCOS): a systematic review and meta-analysis
format:
  pdf: default
  aft-pdf:
    keep-tex: true
author:
  - name: Richard Kirwan
  - name: Leigh Peele
  - name: Greg Nuckols
  - name: Georgia Kohlhoff
  - name: Hannah Cabré
  - name: Alyssa Olenick
  - name: James Steele
abstract: |
  Background: Polycystic ovary syndrome is the most common endocrine condition affecting women of reproductive age. Overweight and obesity in women with PCOS is commonly deemed a result of a lower basal metabolic rate (BMR), which has influenced lifestyle-based interventions in this group. Evidence supporting this reduced, however, is not consistent. Objectives: To systematically search and meta-analyse the existing literature to determine if resting energy expenditure differs between women with and without polycystic ovary syndrome (PCOS). Design: A systematic search was conducted using PubMed, Medline and Web of Science databases from January 1990 to January 2025. Studies that assessed resting energy expenditure in women with and without PCOS were included. Results: 18 studies were identified. Study populations ranged from X to X participants, with mean ages ranging from X to X years. Conclusions: TO ADD
keywords: Polycystic ovary syndrome, PCOS, resting energy expenditure, REE, basal metabolic rate, BMR
pdf-engine: xelatex
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

@@

The main model for mean REE with $\textrm{cond}$ representing the condition (either control or PCOS) was as follows:
$$
\small
\begin{align*}
\hat{\theta}_{ijkl} &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]

\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_[ijkl]
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[10pt]

\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}

\text{, for lab i = 1,} \dots \text{,I} \\[12pt]

\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix}
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})
\text{, for effect l = 1,} \dots \text{,L} \\[12pt]

\end{align*}
$$

@@

$$
\small
\begin{align*}
\beta_0 &\sim \text{Student-}t(3,\, 1441.81,\, 84.56) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 200) \\[12pt]

\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 149.89,\, 82.91) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\,
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 112.4) \\[12pt]

\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{align*}
$$
where the prior for $\beta_{0}$, which corresponded to the model intercept and mean REE in the control condition, was set based on meta-analysis of the mean REEs for women from two large studies of healthy people [@velasquezUseAmmoniaInhalants2011; @pavlidouRevisedHarrisBenedict2023] though set with a conservative degrees of freedom for the $\textrm{Student-}t$ distribution.The random intercept $\sigma^2_{0,study}$ was set similarly to this. The prior for the fixed effect $\beta_{1}$, reflecting the difference between control and PCOS conditions was set based on a wide range of possible values considering the minimum and and maximum values of the ranges reported in the two studies noted (i.e., 2492 - 908 = 1584). We then set a prior that permits values approximately across this range of values with the majority of it's mass centred around zero. The remaining random effects were set based on the default weakly regularising priors for `brms` and scaled to the expected response values using a $\textrm{half-student-}t$ distribution with 3 degrees of freedom and $\mu=0$, and both correlation matrices $\textrm{corr}_{lab}$ and $\textrm{corr}_{study}$ were set with an $\textrm{LKJcorr(1)}$ distribution.

@@

$$
\small
\begin{align*}
\log(\hat{\theta}_{ijkl}) &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]

\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_{[ijkl]}
       + \beta_2\,\tilde{m}_{[ijkl]}
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[8pt]

m &= \log(y_{i,\mathrm{mean,[ijkl]}}) \\[3pt]
\tilde{m} &\sim \mathcal{N}(m,\, \sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2) \\[10pt]

\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}

\text{, for lab i = 1,} \dots \text{,I} \\[12pt]

\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix}
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})
\text{, for effect l = 1,} \dots \text{,L} \\[12pt]
\end{align*}
$$

@@

The priors for this model were as follows:
$$
\small
\begin{align*}
\beta_0 &\sim \text{Student-}t(3,\, 5.54,\, 0.80) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 5.3) \\[4pt]
\beta_2 &\sim \text{Student-}t(3,\, 0,\, 2.5) \\[12pt]

\text{mean}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 7.28,\, 0.62) \\[4pt]
\text{sd}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 0,\, 5) \\[12pt]

\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 1.08,\, 1.06) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\,
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 2.5) \\[12pt]

\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{align*}

$$

@@

$$
\small
\begin{align*}
\hat{\theta}_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma^2_{ij}) \\[6pt]

\mu_{ij} &= \beta_0
       + \alpha_{0,\mathrm{lab}[i]}
       + \alpha_{0,\mathrm{study}[j]} \\[10pt]

\alpha_{0,\mathrm{lab}[i]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{lab}})
\text{, for lab i = 1,} \dots \text{,I} \\[12pt]
\alpha_{0,\mathrm{study}[j]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{study}})
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\end{align*}
$$

@@

```{r}
#| label: fig-mean-REE 
#| fig-width: 10
#| fig-height: 5
#| fig-cap: Posterior distribution, mean point estimates, and 95% quantile intervals for conditional estimates by study, global grand mean estimates by condition, and the contrast between conditions for mean resting energy expenditure of control women without PCOS and women with PCOS.

@@

```{r}
#| label: fig-variance-REE 
#| fig-width: 10
#| fig-height: 5
#| fig-cap: Posterior distribution, variance point estimates, and 95% quantile intervals for conditional estimates by study, global grand variance estimates by condition, and the contrast ratio between conditions for the standard deviation of resting energy expenditure of control women without PCOS and women with PCOS.

@@

>>>>

---
title: |
  Does resting energy expenditure differ between women with and without polycystic ovary syndrome (PCOS): a systematic review and meta-analysis
date: 'format(Sys.time(), "%b %d, %Y")'
format: pdf
author:
  - name: Richard Kirwan
    affiliations:
      - ref: 1
    orcid: 0000-0003-4645-0077
    corresponding: true
    email: R.P.Kirwan@ljmu.ac.uk
  - name: Leigh Peele
    affiliations:
      - ref: 2
    email: leigh@macrofactorapp.com
  - name: Greg Nuckols
    affiliations:
      - ref: 2
    orcid: 0009-0004-2679-7967
    email: greg@macrofactorapp.com
  - name: Georgia Kohlhoff
    affiliations:
      - ref: 3
    # orcid: 0000-0002-8003-0757
    email: g_kohlhoff@hotmail.co.uk
  - name: Hannah Cabré
    affiliations:
      - ref: 4
    orcid: 0000-0002-3235-6867
    email: Hannah.Cabre@pbrc.edu
  - name: Alyssa Olenick
    affiliations:
      - ref: 5
    orcid: 0000-0002-2217-8067
    corresponding: true
    email: alyssaolenickphd@gmail.com
  - name: James Steele
    affiliations:
      - ref: 6
      - ref: 2
      - ref: 7
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
affiliations:
  - id: 1
    name: Research Institute for Sports and Exercise Sciences, Liverpool John Moores Universtiy, Liverpool, UK
  - id: 2
    name: MacroFactor, Stronger by Science LLC, Raleigh, North Carolina, USA
  - id: 3
    name: Flourishing Health, Liverpool, UK
  - id: 4
    name: Reproductive Endocrinology and Women’s Health Research Program, Pennington Biomedical Research Center, Baton Rouge, Louisiana, USA
  - id: 5
    name: Dr Alyssa Olenick LLC
  - id: 6
    name: Steele Research Limited, Eastleigh, Hampshire, UK
  - id: 7
    name: School of Health and Biomedical Sciences, Royal Melbourne Institute of Technology, Melbourne, VIC, Australia
abstract: |
  Background: Polycystic ovary syndrome is the most common endocrine condition affecting women of reproductive age. Overweight and obesity in women with PCOS is commonly deemed a result of a lower basal metabolic rate (BMR), which has influenced lifestyle-based interventions in this group. Evidence supporting this reduced, however, is not consistent. Objectives: To systematically search and meta-analyse the existing literature to determine if resting energy expenditure differs between women with and without polycystic ovary syndrome (PCOS). Design: A systematic search was conducted using PubMed, Medline and Web of Science databases from January 1990 to January 2025. Studies that assessed resting energy expenditure in women with and without PCOS were included. Results: 18 studies were identified. Study populations ranged from X to X participants, with mean ages ranging from X to X years. Conclusions: TO ADD
keywords: Polycystic ovary syndrome, PCOS, resting energy expenditure, REE, basal metabolic rate, BMR
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

@@

The main model for mean REE with $\textrm{cond}$ representing the condition (either control or PCOS) was as follows:
$$
\scriptsize
\begin{aligned}
\hat{\theta}_{ijkl} &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]
\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_[ijkl]
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[10pt]
\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}
\text{, for lab i = 1,} \dots \text{,I} \\[12pt]
\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix}
\text{, for study j = 1,} \dots \text{,J} \\[12pt]
\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})
\text{, for effect l = 1,} \dots \text{,L}
\end{aligned}
$$

@@

$$
\small
\begin{aligned}
\beta_0 &\sim \text{Student-}t(3,\, 1441.81,\, 84.56) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 200) \\[12pt]
\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 149.89,\, 82.91) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\,
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 112.4) \\[12pt]
\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{aligned}
$$
where the prior for $\beta_{0}$, which corresponded to the model intercept and mean REE in the control condition, was set based on meta-analysis of the mean REEs for women from two large studies of healthy people [@velasquezUseAmmoniaInhalants2011; @pavlidouRevisedHarrisBenedict2023] though set with a conservative degrees of freedom for the $\textrm{Student-}t$ distribution.The random intercept $\sigma^2_{0,study}$ was set similarly to this. The prior for the fixed effect $\beta_{1}$, reflecting the difference between control and PCOS conditions was set based on a wide range of possible values considering the minimum and and maximum values of the ranges reported in the two studies noted (i.e., 2492 - 908 = 1584). We then set a prior that permits values approximately across this range of values with the majority of it's mass centred around zero. The remaining random effects were set based on the default weakly regularising priors for `brms` and scaled to the expected response values using a $\textrm{half-student-}t$ distribution with 3 degrees of freedom and $\mu=0$, and both correlation matrices $\textrm{corr}_{lab}$ and $\textrm{corr}_{study}$ were set with an $\textrm{LKJcorr(1)}$ distribution.

@@

$$
\scriptsize
\begin{aligned}
\log(\hat{\theta}_{ijkl}) &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]
\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_{[ijkl]}
       + \beta_2\,\tilde{m}_{[ijkl]}
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[8pt]
m &= \log(y_{i,\mathrm{mean,[ijkl]}}) \\[3pt]
\tilde{m} &\sim \mathcal{N}(m,\, \sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2) \\[10pt]
\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}
\text{, for lab i = 1,} \dots \text{,I} \\[12pt]
\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix}
\text{, for study j = 1,} \dots \text{,J} \\[12pt]
\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})
\text{, for effect l = 1,} \dots \text{,L}
\end{aligned}
$$

@@

The priors for this model were as follows:
$$
\small
\begin{aligned}
\beta_0 &\sim \text{Student-}t(3,\, 5.54,\, 0.80) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 5.3) \\[4pt]
\beta_2 &\sim \text{Student-}t(3,\, 0,\, 2.5) \\[12pt]
\text{mean}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 7.28,\, 0.62) \\[4pt]
\text{sd}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 0,\, 5) \\[12pt]
\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 1.08,\, 1.06) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\,
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 2.5) \\[12pt]
\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{aligned}
$$

@@

$$
\small
\begin{aligned}
\hat{\theta}_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma^2_{ij}) \\[6pt]
\mu_{ij} &= \beta_0
       + \alpha_{0,\mathrm{lab}[i]}
       + \alpha_{0,\mathrm{study}[j]} \\[10pt]
\alpha_{0,\mathrm{lab}[i]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{lab}})
\text{, for lab i = 1,} \dots \text{,I} \\[12pt]
\alpha_{0,\mathrm{study}[j]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{study}})
\text{, for study j = 1,} \dots \text{,J}
\end{aligned}
$$

@@

```{r}
#| label: fig-mean-REE 
#| fig-width: 10
#| fig-height: 7.5
#| fig-cap: Posterior distribution, mean point estimates, and 95% quantile intervals for conditional estimates by study, global grand mean estimates by condition, and the contrast between conditions for mean resting energy expenditure of control women without PCOS and women with PCOS.

@@

```{r}
#| label: fig-variance-REE 
#| fig-width: 10
#| fig-height: 7.5
#| fig-cap: Posterior distribution, variance point estimates, and 95% quantile intervals for conditional estimates by study, global grand variance estimates by condition, and the contrast ratio between conditions for the standard deviation of resting energy expenditure of control women without PCOS and women with PCOS.

@@

# References
